
%!TEX option = --shell-escape

\documentclass[9pt, xcolor={svgnames, x11names},professionalfonts]{beamer}


\input{../../includes/macros}
\input{../../includes/definedColors}
\input{../../includes/Channel.tex}
\input{../../includes/Couple.tex}
\input{../../includes/DL.tex}
\input{../../includes/DLdown.tex}
\input{../../includes/EyeBolt.tex}
\input{../../includes/EyeConnection.tex}
\input{../../includes/Member}
\input{../../includes/Mem}
\input{../../includes/Meme}
\input{../../includes/PC}
\input{../../includes/Ring}
\input{../../includes/Rocker}
\input{../../includes/Roller}
\input{../../includes/Rone}
\input{../../includes/Ronly}
\input{../../includes/Pulley}
\input{../../includes/PulleyB}
\input{../../includes/PulleyC}
\input{../../includes/Luke.tex}
\input{../../includes/Skywalker.tex}
\input{../../includes/WBeam.tex}
% \input{../../includes/includesExisting/tikzObjects.tex}

\setlength{\parindent}{0pt}
\setlength{\parskip}{\medskipamount}
\def\bgcolor{Gainsboro!50}


\tcbset{fonttitle=\itshape\rmfamily}
\usepackage{mathpazo}
\usepackage{amssymb} % for /checkmark
 
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usefonttheme[onlymath]{serif} % this needs to be before structureitalicserif?
\usefonttheme{structureitalicserif} %make titles fancy ;-)


\usecolortheme[named=statsMaroon]{structure}
\setbeamertemplate{navigation symbols}{} % remove navigation symbols
\setbeamertemplate{headline}{\vspace{0.125cm}}
\setbeamertemplate{footline}{ \hfill \insertshorttitle\qquad \insertsection \qquad \insertframenumber/\inserttotalframenumber\quad{ }\vspace{0.125cm}}
\setbeamertemplate{items}[default]
\setbeamertemplate{blocks}[shadow=true]

\setbeamercolor{title}{bg=statsMaroon, fg=Azure}
\setbeamercolor{frametitle}{fg=white, bg=statsMaroon}
\setbeamercolor{background canvas}{bg=Gainsboro!50}
\setbeamercolor{block title}{bg=statsMaroon, fg=white}
\setbeamercolor{block body}{bg=white, fg=black}

\setlength{\parskip}{\medskipamount}
\setlength{\parindent}{0pt}

% https://tex.stackexchange.com/questions/731957/how-to-supress-missing-character-there-is-no-u003b-in-font-nullfont
\tracinglostchars=1
% \hfuzz 120pt

\def\scale{1}
\newcounter{examnumber}
\newcounter{exernumber}
%test
\resetcounteronoverlays{tcb@cnt@myexam}
\resetcounteronoverlays{tcb@cnt@myexer}
% \newcounter{myexercisecounter}

% Title page details: 
\title[08 Method of Sections]{\Huge 08 Method of Sections}
\subtitle[Engineering Statics]{\Large\textcolor{white}{Engineering Statics}}
\author{}
\date{\small Updated on: \today}

% \raggedright

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[plain]    %don't need footer on titlepage
	\titlepage
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{}	
	% \addtocounter{framenumber}{42}
	\begin{myexam}{}{}
		\def\scale{0.675}
		\parb\centering
		\input{../../pikz/08MoS/08MoS01.tex}
		\parb
		\cmini[0.75]{
			\centering
			Use the method of sections to determine the internal forces in members $BC$, $CH$ and $GH$.
		}			
		\pars
		\addtocounter{\tcbcounter}{-1}
	\end{myexam}
\end{frame}
	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}	
	
	\begin{statsbox}[height=5.25cm, top=0mm]{}
		\def\scale{0.825}			
		\centering
		\input{../../pikz/08MoS/08MoS01b.tex}			
	\end{statsbox}
	\parm
	\only<1-7>{
		\begin{statsbox}[height=2.5cm]{The Method of Sections}
			\only<1-4>{
				\begin{itemize}
					\item<1-> The method of sections technique is widely used in engineering. 
					\item<2-> It involves drawing a section $a\!-\!a$ through a structure or member.
					\item<3-> Then the segments on each side of the section are also be in equilibrium.
					\item<4-> The section 'exposes' the internal forces in cut members.				
				\end{itemize}
			}
			\only<5-7>{
				\begin{itemize}				
					\item <5-> We are free to place our section wherever is most convenient.\parm
					\item <6-> We generally look for a section that 'cuts' the members we need. \parm
					\item <7->	Then we choose whichever is the easier of the two segments to analyze.
				\end{itemize}
			}
		\end{statsbox}
	}
		\only<8-9>{
			\begin{myexam}[height=2.5cm, left=0mm]{Solution}{}
				\only<8-9>{
					\begin{itemize}
						\item<8-> The right segment is the easiest to analyze since it only contains a single external force.					
						\item<9-> Note that in this case we only have the one choice since the reactions at $A$ and $G$ are '{\bf statically indeterminate}.' (That is, we can't determine them using only the equilibrium equations. Why is this?) 
						\item <10-> ten			
					\end{itemize}
				}
			\end{myexam}
		}
		\only<10->{
			\begin{myexam}[height=2.5cm, left=0mm]{Solution}{}
				\small
				\only<10>{
					\begin{align*}
						\Sigma M_E &= F_{BC}\cd(1.50\,\textsf{m}) - (850\,\textsf{N})\cd (1.50\,\textsf{m}) = 0\\\\
						\Ra F_{BC} &= 850\,\textsf{N}
					\end{align*}
				}
				\only<11>{
					\begin{align*}
						\Sigma M_B &= -F_{EF}\cd(1.50\,\textsf{m}) - (850\,\textsf{N})\cd (3.00\,\textsf{m}) = 0\\\\
						\Ra F_{EF} &= -1700\,\textsf{N}
					\end{align*}
				}
				\only<12-13>{
					\begin{align*}
						\Sigma F_y &= -F_{BE}\cd\sin 45\deg - 850\,\textsf{N} = 0\\\\
						\Ra F_{BE} &= -1202.1\,\textsf{N}
					\end{align*}
				}
			\end{myexam}
		}
		\only<13->{
			\begin{textblock*}{\columnwidth}(0.875cm,0.125cm)
				\def\modalFill{\bgcolor}
				\input{../../pikz/modalCloud.tex}	
			\end{textblock*}
				
			\only<13->{
				\begin{textblock*}{5cm}(7cm,0.5cm)
					\begin{statsbox}{The Answers}
						\small
						\begin{align*}
							BC &= 850\,\textsf{N}\quad\textsf{(Tension)}\\[0.25em]
							BE &= 1200\,\textsf{N}\quad\textsf{(Compression)}\\[0.25em]
							EF &= 1700\,\textsf{N}\quad\textsf{(Compression)}
						\end{align*}
						\par
					\end{statsbox}
				\end{textblock*}
			}
			
			\only<14->{
				\begin{textblock*}{9cm}(3cm,3cm)
					\begin{statsbox}[left = 0mm, right=2mm]{Note:}
						\small
						\begin{enumerate}
							\item<14-> If any structure (not only a truss) is in equilibrium, then any section will cut it into two segments, each of which is itself in equilibrium. 
							\item<15-> To solve for more than three truss members, it is necessary to repeat the method of sections using a different section (one that cuts the additional members required by the problem).
							\item<16-> We can use all three equilibrium equations $\Sigma M = 0$, $\Sigma F_x=0$ and $\Sigma F_y=0$ but it is often less work to take moments about conveniently located joints.
							\item<17> It is not necessary to take moments using joints in the 'active' segment. Moments can be taken about anywhere on the truss -- or even anywhere on the plane in which the truss is situated. If a structure is in equilibrium, its moments about any point in the plane still sum to zero.
						\end{enumerate}
					\end{statsbox}
				\end{textblock*}
			}	
		}
		% \addtocounter{framenumber}{0}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{}
	\def\scale{0.5}
	\begin{myexam}{}{}
		\parb\centering
		\input{../../pikz/08MoS/08MoS02.tex}
		\pars
		Use the method of sections to determine the internal forces in members $BC$, $CH$ and $GH$.
		\pars
	\end{myexam}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{}
	\def\scale{0.5125}
	\begin{myexam}{}{}
		\parb\centering
		\input{../../pikz/08MoS/08MoS06.tex}
		\pars
		Use the method of sections to determine the internal forces in members $BC$, $CH$ and $GH$.
		\pars
	\end{myexam}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{}
	\def\scale{0.5125}
	\begin{myexer}{}{}
		\parb\centering
		\input{../../pikz/08MoS/08MoS07.tex}
		\pars
		An alternative design is being considered for the previous example. 
		Use the method of sections to determine the internal forces in members $BC$, $BG$ and $GH$. How do they compare to the previous results?
		\pars
	\end{myexer}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{}
	\def\scale{0.45}
	\begin{myexam}{}{}
		\parb\centering
		\input{../../pikz/08MoS/08MoS05.tex}
		\parb
		Determine the internal force in $DJ$.
		\pars
	\end{myexam}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{}
	\def\scale{0.575}
	
	\begin{myexam}{}{}
		\vspace{-1em}
		\mini[0.5]{
			\parb\centering
			\input{../../pikz/08MoS/08MoS04.tex}		
		}
		\hfill
		\mini[0.4]{
			Determine the forces in members $AB$ and $GH$.		
		}
	\end{myexam}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{}
	\def\scale{0.5}
	\begin{myexam}{}{}
		\parb\centering
		\input{../../pikz/08MoS/08MoS08.tex}
		\pars
		Use the method of sections to determine the internal forces in members $EF$, $EQ$, $LM$ and $MQ$.
		\pars
	\end{myexam}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{}
	\def\scale{0.575}
	
	\begin{myexer}{}{}		
			\centering
			\input{../../pikz/08MoS/08MoS03.tex}
			\parb		
			Determine the forces in members $CF$, $CG$,$EG$ and $EH$.
			\parb		
		
	\end{myexer}

\end{frame}

%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}