
%!TEX option = --shell-escape

\documentclass[9pt, xcolor={svgnames, x11names},professionalfonts]{beamer}


\input{../../includes/macros}
\input{../../includes/definedColors}
\input{../../includes/Channel.tex}
\input{../../includes/Couple.tex}
\input{../../includes/DL.tex}
\input{../../includes/DLdown.tex}
\input{../../includes/EyeBolt.tex}
\input{../../includes/EyeConnection.tex}
\input{../../includes/Member}
\input{../../includes/Mem}
\input{../../includes/Meme}
\input{../../includes/PC}
\input{../../includes/Ring}
\input{../../includes/Rocker}
\input{../../includes/Roller}
\input{../../includes/Rone}
\input{../../includes/Ronly}
\input{../../includes/Pulley}
\input{../../includes/PulleyB}
\input{../../includes/PulleyC}
\input{../../includes/Luke.tex}
\input{../../includes/Skywalker.tex}
\input{../../includes/WBeam.tex}
% \input{../../includes/includesExisting/tikzObjects.tex}

% \setlength{\parindent}{0pt}
% \setlength{\parskip}{\medskipamount}
\def\bgcolor{Gainsboro!50}


\tcbset{fonttitle=\itshape\rmfamily}
\usepackage{mathpazo}
\usepackage{amssymb} % for /checkmark
 
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usefonttheme[onlymath]{serif} % this needs to be before structureitalicserif?
\usefonttheme{structureitalicserif} %make titles fancy ;-)


\usecolortheme[named=statsMaroon]{structure}
\setbeamertemplate{navigation symbols}{} % remove navigation symbols
\setbeamertemplate{headline}{\vspace{0.125cm}}
\setbeamertemplate{footline}{ \hfill \insertshorttitle\qquad \insertsection \qquad \insertframenumber/\inserttotalframenumber\quad{ }\vspace{0.125cm}}
\setbeamertemplate{items}[default]
\setbeamertemplate{blocks}[shadow=true]

\setbeamercolor{title}{bg=statsMaroon, fg=Azure}
\setbeamercolor{frametitle}{fg=white, bg=statsMaroon}
\setbeamercolor{background canvas}{bg=Gainsboro!50}
\setbeamercolor{block title}{bg=statsMaroon, fg=white}
\setbeamercolor{block body}{bg=white, fg=black}

\setlength{\parskip}{\medskipamount}
\setlength{\parindent}{0pt}

% https://tex.stackexchange.com/questions/731957/how-to-supress-missing-character-there-is-no-u003b-in-font-nullfont
\tracinglostchars=1
% \hfuzz 120pt

\def\scale{1}
\newcounter{examnumber}
\newcounter{exernumber}
%test
\resetcounteronoverlays{tcb@cnt@myexam}
\resetcounteronoverlays{tcb@cnt@myexer}
% \newcounter{myexercisecounter}

% Title page details: 
\title[09 Complex Frames]{\Huge 09 Complex Frames}
\subtitle[Engineering Statics]{\Large\textcolor{white}{Engineering Statics}}
\author{}
\date{\small Updated on: \today}

% \raggedright

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[plain]    %don't need footer on titlepage
	\titlepage
\end{frame}

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Simple Frames}
 	\begin{textblock*}{10cm}(1.5cm,1cm)
  	\begin{itemize}
			\item  In the problems we investigated in the module on the equilibrium of rigid bodies, there was  a structural member, acted upon by a force, or forces, each with a known magnitude and direction (such as weight and/or applied loads). \parm
			\item There was a single force with a known direction but unknown magnitude (such as a hydraulic hoist, or a chain in tension,\ldots) and a reaction with unknown $x$- and $y$-components.\parm
			\item We are limited, by the equations of equilibrium, to solving for a maximum of three unknowns. These problems can be considered {\bf simple frames}.
  	\end{itemize}
 	\end{textblock*}

 \def\scale{0.45}
 \begin{textblock*}{4cm}( 1.75cm, 6cm )	
  	\input{../../pikz/06ERB/06erb20b.tex}
 \end{textblock*}
 %
 \def\scale{0.325}
 \begin{textblock*}{4cm}(7.5cm, 6cm)
  \input{../../pikz/06ERB/06erb09b.tex}
 \end{textblock*}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Statical Determinancy}
 \begin{textblock*}{1\textwidth}(1cm, 1.5cm)
  \centering
  \def\scale{0.625}
  \input{../../pikz/09CF/09CF09a}
 \end{textblock*}

 \begin{textblock*}{1\textwidth}(1cm, 5.5cm)
  \only<1->{
   There is a fixed connection at $C$. We have solved problems like this.\par
  }
  \only<2->{
   But how about now? How many unknowns are there?}
  \only<3->{
   {\bfseries \!Four!}\par
  }
  \only<4->{
   With the three equations of statics, we can only solve for three unknowns. We cannot solve this with statics alone. This is a {\bfseries statically indeterminant} problem. \par
  }
  \only<5->{
  But this is a complex frame and we {\bf can} solve this!\parm
  }
  
 \end{textblock*}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{}

	\only<1>{
		\begin{myexam}{}{}
			\centering
			\def\bgcolor{white}
			\def\scale{0.625}
			\input{../../pikz/09CF/09CF21.tex}
			\parb
			There is a rocker at $A$, a pinned connection at $B$ and a fixed connection at $C$. Determine the reactions at $A$ and $C$.
			\addtocounter{\tcbcounter}{-1}
		\end{myexam}
	}
	
	\begin{textblock*}{1\textwidth}(1cm,0.25cm)
		\only<2->{	
			\def\scale{0.562}
			\begin{statsbox}[height=3.75cm,top=0mm]{}
				\centering
				\vspace{-0.375em}
				\input{../../pikz/09CF/09CF22.tex}
			\end{statsbox}
		}	
	\end{textblock*}
	\begin{textblock*}{1\textwidth}(1cm,4.25cm)
		\only<2-3>{				
			\begin{myexam}[height=4.325cm]{Solution}{}
				\parb
				\begin{enumerate}
					\item How many unknowns are there?
					\only<3->{
						\parb Notice that member $AB$ exerts an equal and opposite force (with components $B_x$ and $B_y$) on member $BC$. This is a necessary condition for equilibrium at $B$.\parb
						$A_y$, $B_x$, $B_y$, $C_x$, $C_y$ and $M_C$ makes 6 unknowns.
					}
					\addtocounter{\tcbcounter}{-1}
					\suspend					
				\end{enumerate}
				
			\end{myexam}
		}	
	\end{textblock*}
	\begin{textblock*}{1\textwidth}(1cm,4.25cm)
		\only<4-6>{				
			\begin{myexam}[height=4.325cm]{Our Method}{}
				\raggedright\parb
				Consider a vertical section through $B$.
				\parm
				\only<5->{
				The portion to the left of the section (that is, member $AB$) is in equilibrium. It has three unknowns: $A_y$, $B_x$ and $B_y$. We can solve for these.
				}
				\parm
				\only<6->{
					The portion to the right of the section (member $BC$), now that we know $B_x$ and $B_y$, has three remaining unknowns: $M_C$, $C_x$ and $C_y$. We can solve for these.
				}	
			\end{myexam}
		}			
	\end{textblock*}
	\begin{textblock*}{1\textwidth}(1cm,4.25cm)
		\only<7->{				
			\begin{myexam}[height=4.325cm]{Solution}{}
				\parb				
				\begin{enumerate}
					\resume
					\item Draw members separated for analysis.
					\only<8->{
						\item Resolve the distributed loads
					}
					\addtocounter{\tcbcounter}{-1}					
				\end{enumerate}
			\end{myexam}
		}	
	\end{textblock*}

 
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}