
%!TEX option = --shell-escape

\documentclass[9pt, xcolor={svgnames, x11names},professionalfonts]{beamer}


\input{../../includes/macros}
\input{../../includes/definedColors}
\input{../../includes/Channel.tex}
\input{../../includes/Couple.tex}
\input{../../includes/DL.tex}
\input{../../includes/EyeBolt.tex}
\input{../../includes/EyeConnection.tex}
\input{../../includes/Member}
\input{../../includes/Mem}
\input{../../includes/Meme}
\input{../../includes/PC}
\input{../../includes/Ring}
\input{../../includes/Rocker}
\input{../../includes/Roller}
\input{../../includes/Rone}
\input{../../includes/Ronly}
\input{../../includes/Pulley}
\input{../../includes/PulleyB}
\input{../../includes/PulleyC}
\input{../../includes/Luke.tex}
\input{../../includes/Skywalker.tex}
\input{../../includes/WBeam.tex}
% \input{../../includes/includesExisting/tikzObjects.tex}

\setlength{\parindent}{0pt}
\setlength{\parskip}{\medskipamount}
\def\bgcolor{Gainsboro!50}


\tcbset{fonttitle=\itshape\rmfamily}
\usepackage{mathpazo}
\usepackage{amssymb} % for /checkmark
 
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usefonttheme[onlymath]{serif} % this needs to be before structureitalicserif?
\usefonttheme{structureitalicserif} %make titles fancy ;-)


\usecolortheme[named=statsMaroon]{structure}
\setbeamertemplate{navigation symbols}{} % remove navigation symbols
\setbeamertemplate{headline}{\vspace{0.125cm}}
\setbeamertemplate{footline}{ \hfill \insertshorttitle\qquad \insertsection \qquad \insertframenumber/\inserttotalframenumber\quad{ }\vspace{0.125cm}}
\setbeamertemplate{items}[default]
\setbeamertemplate{blocks}[shadow=true]

\setbeamercolor{title}{bg=statsMaroon, fg=Azure}
\setbeamercolor{frametitle}{fg=white, bg=statsMaroon}
\setbeamercolor{background canvas}{bg=Gainsboro!50}
\setbeamercolor{block title}{bg=statsMaroon, fg=white}
\setbeamercolor{block body}{bg=white, fg=black}

\setlength{\parskip}{\medskipamount}
\setlength{\parindent}{0pt}

% https://tex.stackexchange.com/questions/731957/how-to-supress-missing-character-there-is-no-u003b-in-font-nullfont
\tracinglostchars=1
% \hfuzz 120pt

\def\scale{1}
\newcounter{examnumber}
\newcounter{exernumber}
%test
\resetcounteronoverlays{tcb@cnt@myexam}
\resetcounteronoverlays{tcb@cnt@myexer}
% \newcounter{myexercisecounter}

% Title page details: 
\title[06 Equilibrium of Rigid Bodies]{\Huge 06 Equilibrium of Rigid Bodies}
\subtitle[Engineering Statics]{\Large\textcolor{white}{Engineering Statics}}
\author{}
\date{\small Updated on: \today}

% \raggedright

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[plain]    %don't need footer on titlepage
	\titlepage
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Overview}
	\cmini[0.8]{
		\raggedright
		\begin{itemize}
			\item Much of the study of statics involves the calculations of reaction forces generated between a structural body and its supports when loads are applied.
			\item[]\item There are various connection types used between a structural body and its supports. These connections influence the direction and the sense of the reaction. We shall examine some of these connections now.
		\end{itemize}
	}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Types of Connections: Cable}
	\def\scale{0.5}
	\begin{textblock*}{\textwidth}(1cm, 1.5cm)
		\centering
		\input{../../pikz/06ERB/cableConnection}
	\end{textblock*}

	\begin{textblock*}{\textwidth}(1cm, 5.5cm)
		\cmini[0.9]{
			When a structural member or body is supported by a cable (or rope or chain), the cable is assumed to be weightless (and consequently straight) and the cable exerts a reaction on the structural member {\bf in the same direction} as the cable. \parm
			A cable is in tension and can only {\bf pull}; it cannot push. \parm
			There is only one unknown: the magnitude of the force. The direction and sense of the force are known.
		}
	\end{textblock*}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Types of Connections: Strut}
	\def\scale{0.4}
	\begin{textblock*}{\textwidth}(1cm, 1.5cm)
		\centering
		\input{../../pikz/06ERB/strutConnection}
	\end{textblock*}

	\begin{textblock*}{\textwidth}(1cm, 4.75cm)
		\cmini[0.95]{
			Like a cable, a straight strut (or link) exerts a reaction on a structural member in the direction of the strut. Unlike a cable, a strut can pull  or push.
			\parm
			If we don't know whether a strut is pushing or pulling, we generally assume that the reaction is directed away from the structural member (pulling, in tension), as shown in (a). If our calculations then determine that $F$ is negative, the direction is opposite to our assumption (i.e., pushing) (b).
			\parm
			As with the cable, there is only one unknown. The sign of $F$ determines the  sense of $F$.
		}
	\end{textblock*}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Types of Connections: Roller}
	% \begin{textblock*}{\textwidth}(1cm, 1.5cm)
	% 	\centering
	% 	(A table of connection types is shown on page 202 of your text.)\parm
	% \end{textblock*}
	\def\scale{0.45}
	\begin{textblock*}{\textwidth}(1cm, 1.75cm)
		\centering
		\input{../../pikz/06ERB/rollerConnection}
	\end{textblock*}

	\begin{textblock*}{\textwidth}(1cm, 5cm)
		\cmini[0.95]{
			A roller (assumed weightless and frictionless) can provide no resistance {\bfseries along} the slope on which it is resting.
			\uncover<2>{ The only reaction a roller can provide is {\bfseries perpendicular} to the slope.
				\parm
				A roller can only push. It is not fixed to the sloped surface and would lift off the surface if pulled.
				\parm
				As with the cable, there is only one unknown. If your math is correct, the sign of $F$ should always be positive.
			}
		}
	\end{textblock*}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Types of Connections: More Rollers}
	\def\scale{0.35}
	\begin{textblock*}{\textwidth}(1cm, 2cm)
		\input{../../pikz/06ERB/rollerConnectionMore}
	\end{textblock*}

	\begin{textblock*}{\textwidth}(1cm, 6cm)
		\cmini[0.95]{
			Rollers come in different shapes. But they all react in the same way.
			\parb
			\uncover<2>{ The reaction force is perpendicular to the surface that the roller bears on.	}
		}
	\end{textblock*}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Types of Connections: Rockers and Smooth Surfaces}
	\def\scale{0.35}
	\begin{textblock*}{\textwidth}(1cm, 2cm)
		\input{../../pikz/06ERB/rockerConnection}
	\end{textblock*}

	\begin{textblock*}{\textwidth}(1cm, 5cm)
		\cmini[0.95]{
			Two more connection types that react in the same way as rollers:
			\parb
			\uncover<2>{
				The {\bfseries rocker}: the reaction force is perpendicular to the surface that the rocker bears on.	\parm
				The {\bfseries smooth surface} has no friction along the surface: the reaction force is perpendicular to the smooth surface that the structural member bears on.
			}
		}
	\end{textblock*}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Types of Connections: Roller in Smooth Slot}
	% \begin{textblock*}{\textwidth}(1cm, 1.5cm)
	% 	\centering
	% 	(A table of connection types is shown on page 202 of your text.)\parm
	% \end{textblock*}
	\def\scale{0.45}
	\begin{textblock*}{\textwidth}(1cm, 1.5cm)
		\centering
		\input{../../pikz/06ERB/slotConnection}
	\end{textblock*}

	\begin{textblock*}{\textwidth}(1cm, 5.5cm)
		\cmini[0.9]{
			With a roller in a smooth slot, we don't necessarily know whether the roller is:
			\begin{itemize}
				\item<2-> Bearing on the lower smooth surface; in this case it is the lower surface that provides the reaction.
				\item<3-> Bearing on the upper smooth surface; in this case it is the upper surface that provides the reaction.
				\item<4-> In each case, the reaction is perpendicular to the bearing surface of the slot.
			\end{itemize}

		}
	\end{textblock*}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Types of Connections: Pinned Connection}
	% \begin{textblock*}{\textwidth}(1cm, 1.5cm)
	% 	\centering
	% 	(A table of connection types is shown on page 202 of your text.)\parm
	% \end{textblock*}
	\def\scale{0.45}
	\begin{textblock*}{\textwidth}(1cm, 1.5cm)
		\centering
		\input{../../pikz/06ERB/pinnedConnection}
	\end{textblock*}

	\begin{textblock*}{\textwidth}(1cm, 5.5cm)
		\cmini[0.9]{
			With the pinned connection (also known as a hinged connection), movement is restricted in all directions. The reaction can be in any direction.
			\begin{itemize}
				\item<2->This gives us {\bfseries two} unknowns: one generally an $x$-component and one generally a $y$-component.
				\item<3-> Alternatively (and equivalently), the reaction can be specified by a magnitude and a direction. This is the form that we use to describe the reaction.
			\end{itemize}

		}
	\end{textblock*}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Types of Connections: Fixed Connection}
	\def\scale{0.45}
	\begin{textblock*}{\textwidth}(1cm, 1.5cm)
		\centering
		\input{../../pikz/06ERB/fixedConnection}
	\end{textblock*}

	\begin{textblock*}{\textwidth}(1cm, 5.5cm)
		\cmini[0.9]{
			The fixed connection has {\bfseries three} unknowns.
			\begin{itemize}
				\item<2-> Components in the $x$ and $y$ directions (like the pinned connection).
				\item<3-> A reacting moment, $M$, since (unlike the pinned connection) there can be no rotation about the connection.
			\end{itemize}

		}
	\end{textblock*}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Equilibrium: The Rules}

	\cmini[0.95]{
		\begin{itemize}
			\item Here we add another major part of the puzzle: the third and final equation that, combined with our results from the equilibrium of concentric forces, allows us analyze the equilibrium of rigid bodies.\par
			\item In our discussion of force couples, we noted that although $\Sigma F_x=0$ and $\Sigma F_y=0$ there was still some tendency for the force couple to cause rotation.\par
			\item For a system to be in equilibrium, there must be no net moment: the sum of the moments of the forces acting upon a rigid body must be zero. There must be no tendency to rotate.
		\end{itemize}
		\cmini[0.55]{
			\begin{tcolorbox}[colback=white,colframe=structure,left=3pt, top=5pt, bottom=5pt, right=0pt, enhanced, drop fuzzy shadow,center title, title=General Conditions for Equilibrium \lb of Rigid Bodies]
				\vspace{-0.3cm}
				\begin{align*}
					\Sigma F_x & = 0 \\
					\Sigma F_y & = 0 \\
					\Sigma M   & = 0
				\end{align*}

			\end{tcolorbox}
		}
	}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{In Practice:}
	\cmini[0.9]{
		\begin{itemize}
			\item In general, we use these equations to find the reactions at connections between a rigid body (not just a particle) and a support.\parm
			\item Often, these support reactions will have three unknowns: a pinned connection with two unknown components; and a connection with a known direction (roller, cable, two-force member, etc.) but an unknown magnitude (and, possibly, unknown sense).\parm
			\item Usually, our first step  after drawing the FBD {\bfseries (!)} is to take moments about the pinned connection to solve directly for the third unknown (the magnitude of the connection with the known direction).\parm
			\item Then we sum the $x$-components of all the forces involved to solve for the $x$-component of the reaction at the pinned connection. We do the same for the $y$-component. \parm
			\item From the components of the reaction at the pinned connection, $R_x$ and $R_y$, we use the Pythagorean Theorem and the inverse tangent function to find the magnitude $R$ and direction $\theta$ of the reaction.
		\end{itemize}
	}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
	\begin{textblock*}{1\textwidth}(1cm, 0.25cm)

		\begin{myexam}{}{}
			\centering
			\def\scale{0.55}
			\input{../../pikz/06ERB/06erb14.tex}
			\parb
			Determine the tension in the chain and the reaction at $A$.
			% \begin{center}
			% 	\footnotesize
			% 	\rotatebox[origin=c]{180}{
			% 		\textcolor{gray}{
			% 			($T=2.08\,\text{kN,}R_A=5.75\,\text{kN at} 85.5\deg$.)
			% 		}
			% 	}
			% \end{center}
		\end{myexam}
	\end{textblock*}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
	\begin{textblock*}{1\textwidth}(1cm, 0.25cm)

		\begin{myexam}{}{}
			\centering
			\def\scale{0.55}
			\input{../../pikz/06ERB/06erb01.tex}
			\parb
			Determine the reactions at $A$ and at $B$.
			% \begin{center}
			% 	\footnotesize
			% 	\rotatebox[origin=c]{180}{
			% 		\textcolor{gray}{
			% 			($R_B=1.71\,\text{kN at}117\deg,\,R_A=1.93\,\text{kN at }66.7\deg$)
			% 		}
			% 	}
			% \end{center}
			% \addtocounter{\tcbcounter}{-1}
		\end{myexam}
	\end{textblock*}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
	\begin{textblock*}{1\textwidth}(1cm, 0.25cm)

		\begin{myexer}{}{}
			\def\scale{0.8}
			\centering
			\input{../../pikz/06ERB/06erb04.tex}
			\cmini[0.8]{
				\centering
				Determine the reactions at $A$ and $D$.
			}
			% answers, gray, centered, upside down
			% \begin{center}
			% 	\footnotesize
			% 	\textcolor{gray}{
			% 		\rotatebox[origin=c]{180}{
			% 			$\left( R_D=2.79\text{ kN at } 115^\circ,\;R_A=1.08\text{ kN at } 152^\circ \text{, ccw from +ve $x$-axis.} \right)$
			% 		}
			% 	}
			% \end{center}
		\end{myexer}
	\end{textblock*}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{frame}
% 	\begin{textblock*}{1\textwidth}(1cm, 0.25cm)

% 		\begin{myexam}{Solution}{}
% 			\footnotesize
% 			First, as always, the free body diagram:
% 			\begin{center}
% 				\def\scale{0.55}
% 				\input{../../pikz/06ERB/06erb01SolnA.tex}
% 			\end{center}
% 			\parm
% 			\raggedright
% 			We have three unknowns: $R_{Ax}$, $R_{Ay}$ and $R_B$. Start by taking moments about $A$:
% 			\begin{align*}
% 				\Sigma M_A      & = (R_B \cos 26.6\deg\,\text{kN}) (8.00\,\text{m})-(3.30\,\text{kN})(3.20\,\text{m})                        \\
% 				                & \qquad -(R_B \sin 26.6\deg\,\text{kN}) (2.15\,\text{m})                                                    \\
% 				                & = 0                                                                                                           \\
% 				\Rightarrow R_B & = \frac{(3.30\,\text{kN})(3.20\,\text{m})}{(8.00\cos 26.6\deg\,\text{m})-(2.15\sin 26.6\deg\,\text{m})} \\
% 				                & = 1.7058\,\text{kN}
% 			\end{align*}
% 			$$ \bm{R_B=1.71\,\text{\bfseries kN at }117\deg}$$
% 			\addtocounter{\tcbcounter}{-1}
% 		\end{myexam}
% 	\end{textblock*}

% \end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{frame}
% 	\begin{textblock*}{1\textwidth}(1cm, 0.25cm)
% 		\footnotesize
% 		\begin{myexam}{Solution (cont'd)}{}
% 			Now, sum the $y$ components to find $R_y$:
% 			\begin{align*}
% 				\Sigma F_y         & = R_{Ay}-3.3\,\text{kN}+1.7058\cos 26.6\degree\,\text{kN} = 0 \\
% 				\Rightarrow R_{Ay} & = 1.7748\,\text{kN}                                           \\\\
% 				\Sigma F_x         & = R_{Ax}-1.7058\sin 26.6\degree\,\text{kN} = 0                \\
% 				\Rightarrow R_{Ax} & = 0.76379\,\text{kN}
% 			\end{align*}
% 			At this point, there is an opportunity to check our work so far. If we take moments about anywhere (except about $A$ which we've already set to zero), they should sum to zero. Taking moments about $B$ is the most convenient:
% 			\begin{align*}
% 				\Sigma M_B & = (3.30\,\text{kN})(4.80\,\text{m})-(1.7748\,\text{m})(8.00\,\text{m}) \\
% 				           & \qquad\qquad-(0.76379\,\text{m})(2.15\,\text{m})                       \\
% 				           & = -0.000549                                                            \\
% 				           & \approx 0 \qquad\text{\textcolor{mucus}{\checkmark}}
% 			\end{align*}




% 			\addtocounter{\tcbcounter}{-1}

% 		\end{myexam}
% 	\end{textblock*}

% \end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{frame}
% 	\begin{textblock*}{1\textwidth}(1cm, 0.25cm)

% 		\begin{myexam}{Solution (cont'd)}{}
% 			\footnotesize
% 			Find the resultant of the reaction at $A$ from its two components. (We have done this before when studying the resultant of force vectors.)\parb
% 			\centering
% 			\tikz[scale=0.75]{
% 				\draw[-latex, thick] (0,0) -- node[fill=white, above, sloped]{$1.7748\,\text{kN}$}+(0,3.4);
% 				\draw[-latex, thick] (0,0) -- node[fill=white, below, outer sep=0.65mm]{$0.76379\,\text{kN}$}+(1.6,0);
% 				\draw[-latex, thick, saitMaroon] (0,0) -- +(1.6,3.4);
% 				\node at (0.35,0.25) {$\theta$};
% 			}
% 			\begin{align*}
% 				R_A    & = \sqrt{(1.7748\,\text{kN})^2+(0.76379\,\text{kN})^2} \\
% 				       & = 1.9322\,\text{kN}                                   \\\\
% 				\theta & = \tan^{-1}\left[\frac{1.7748}{0.76379}\right]        \\
% 				       & = 66.715\degree
% 			\end{align*}

% 			$$ \bm{R_A=1.93\,\text{\bfseries kN at }66.7\degree}$$
% 		\end{myexam}
% 	\end{textblock*}

% \end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
	\begin{textblock*}{1\textwidth}(1cm, 0.25cm)

		\begin{myexer}{}{}
			\def\scale{0.475}
			\centering
			\input{../../pikz/06ERB/06erb03.tex}
			\cmini[0.8]{
				\centering
				Determine the reactions at the pinned connection and the tension in the cable.
			}
			% answers, gray, centered, upside down
			% \begin{center}
			% 	\footnotesize
			% 	\textcolor{gray}{
			% 		\rotatebox[origin=c]{180}{
			% 			$\left( R_D=12.9\text{ kN},\;R_A=6.75\text{ kN at } 197^\circ \text{, ccw from +ve $x$-axis.} \right)$
			% 		}
			% 	}
			% \end{center}


		\end{myexer}
	\end{textblock*}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
	\begin{textblock*}{1\textwidth}(1cm, 0.25cm)

		\begin{myexam}{}{}
			\def\scale{1}
			\centering
			\input{../../pikz/06ERB/06erb16.tex}
			\cmini[0.8]{

				The roller and the pinned connection are on slopes inclined at $21\deg$ to the horizontal; they are both at the same elevation.\parm
				Determine the reaction at each connection. Indicate direction by measuring counter-clockwise from the positive $x$-axis.
			}
			% answers, gray, centered, upside down
			% \begin{center}
			% 	\footnotesize
			% 	\textcolor{gray}{
			% 		\rotatebox[origin=c]{180}{
			% 			$\left(  \right)$
			% 		}
			% 	}
			% \end{center}
		\end{myexam}
	\end{textblock*}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{}
	\begin{myexam}{}{}
		\def\scale{0.55}
		\input{../../pikz/06ERB/06erb02.tex}
		\parb\centering
		The roller at $B$ is in a smooth slot.\par
		Determine the reactions at $A$ and $B$.
		% answers, gray, centered, upside down
		% \begin{center}
		% 	\footnotesize
		% 	\textcolor{gray}{
		% 		\rotatebox[origin=c]{180}{
		% 			$\left(R_B=301\thinspace\text{N at } \mathsf{270^\circ}, R_A=1280\thinspace\text{N at }\mathsf{117^\circ}\text{, both ccw from +ve }x\text{-axis}\right) $
		% 		}
		% 	}
		% \end{center}
	\end{myexam}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
	\begin{textblock*}{1\textwidth}(1cm, 0.25cm)

		\begin{myexam}{}{}
			\def\scale{0.75}
			\centering
			\input{../../pikz/06ERB/06erb15.tex}
			\parm
			
			$55$-kg bar $AB$ has its centre of gravity at $G$. It is supported by a pinned connection at $A$ and a smooth peg at $C$. A cable is attached at $B$ and has a tensile force of $1.70\,$kN. The direction of the cable varies between $\theta=60\deg$ and $\theta=135\deg$. \parm

			What are the maximum reactions at $A$ and $C$?\parb
			
		\end{myexam}
	\end{textblock*}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{}
	\begin{myexam}{}{}
		\cmini[0.95]{
			\def\scale{0.8}
			\centering
			\input{../../pikz/06ERB/06erb08.tex}
			
			Beam $AB$ has a fixed support at $A$. (Fixed supports offer resistance to rotation in the form of a reacting couple at $A$; clearly, without this, equilibrium would not be possible.)\parm

			Determine the reaction and the reacting couple at $A$.		
		}	
	\end{myexam}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Fixed Supports}
	\begin{myexer}{}{}
		\centering\def\scale{0.75}
		\input{../../pikz/06ERB/06erb10.tex}
		\parb
		Determine the reactions at $A$.
		
	\end{myexer}
\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{}
	\begin{myexam}{}{}
		\centering
		\def\scale{1}
		\input{../../pikz/06ERB/06erb06.tex}
		\parb
		Pipe racks ($AB$, and two hidden behind it) support two smooth Schedule 40 pipes, with an outside diameter of $508\,\text{mm}$, as shown. The pipes are $10\,\text{m}$ in length with a mass of $78.5\,\text{kg/m}$, Each rack supports one-third of the weight of each pipe.\parm 
		Determine the reaction at the fixed connection $A$.
		
	\end{myexam}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{}
	\begin{myexer}{}{}
		\centering
		\def\scale{0.65}
		\input{../../pikz/06ERB/06erb09.tex}
		\parb
		A section of smooth pipe, centred at $O$, has a diameter of $457\,\text{mm}$ and a mass of $186\,\text{kg}$. It is secured by vertical structural member $AB$, hinged with a pinned connection at $A$ and held in place by chain $BC$. \parm Determine the tension in the chain, and the reaction at $A$.		
		
	\end{myexer}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Notes:}
	\cmini[0.9]{
		\begin{enumerate}
			\item  For a body in equilibrium, $\Sigma M=0$ for moments summed about {\bfseries any} point in the plane containing the body.\pars
			\item We have used all the three equations of statics to solve for three unknowns. It would also have been possible to solve using $\Sigma M=0$ three times by choosing appropriate points about which to take moments. There are occasions when it is more convenient to sum moments two or three times, rather than summing components. (We will see this when using the Method of Sections to analyze forces in truss members.)\pars
			\item Since there are only three equations for statics, we can only solve a system for three unknowns. Frequently, two unknowns come from a pinned connection and the third from a cable, roller or some other connection whose reaction direction is known. (Alternatively, we can solve for a fixed connection, which has three unknowns.)\pars
			\item Generally, we start by taking moments about the pinned connection - so that we don't need to consider the moments of the pinned connection unknowns. Then, the moment equation will immediately give a solution for the third unknown, e.g., for a connection with a known force direction.
		\end{enumerate}

	}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Two-Force Members}

	\mini[0.4]{
		For a member with only two external forces acting upon it to be in equilibrium:\parm
		\begin{itemize}
			\item Both forces must share the same line of action
			\item Both forces must have the same magnitude
			\item The forces must have opposite directions
		\end{itemize}
		\parm
		Then, $\Sigma F_x=0 $, $\Sigma F_y=0 $ {\bfseries and} there is no tendency for the member to rotate.
		\parm
		Strut connections and cables are two-force members!

	}
	\hfill
	\mini[0.5]{
		\def\scale{0.75}
		\tcb{
			\input{../../pikz/06ERB/tenscomp1.tex}
		}
	}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Straight Two-Force Members}
	\def\scale{0.75}
	In straight two-force members, the lines of action of the forces are along the member.\lb The forces shown here are {\bfseries external} forces applied to the member.
	\begin{center}
		\tcb{
			\input{../../pikz/06ERB/tenscomp2.tex}
		}
	\end{center}

	\uncover<2->{
		These external forces generate corresponding {\bfseries internal} forces which can be examined by `cutting' a section through the member:
		\begin{center}
			\tcb{
				\input{../../pikz/06ERB/tenscomp3.tex}
			}
		\end{center}
	}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{External and Internal Forces}
	\def\scale{0.65}
	\cmini[1]{
		It is important to distinguish between external and internal forces.

		When a two-force member is in tension, external forces pull {\bfseries away} from the member (attempting to make the member longer). The opposite is true for compression.
		\parb\centering
		
		\begin{statsbox}[width=0.65\linewidth]{External Forces}
			\centering
			\input{../../pikz/06ERB/tenscomp4.tex}
		\end{statsbox}

		\parb
	
		\begin{statsbox}[width=0.65\linewidth]{Internal Forces} 
			\centering
			\input{../../pikz/06ERB/tenscomp5.tex}
		\end{statsbox}
	
	}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{External and Internal Forces}
	\def\scale{0.65}
	\cmini[1]{
		Initially, the direction of internal forces may seem counter-intuitive.

		% In order to maintain equilibrium,
		% the internal force in the member is in the \textbf{opposite} direction. In tension, the {\bfseries internal} force in the member pulls \textbf{away} from the joint. In compression, the {\bfseries internal} force in the member pushes  \textbf{towards} the joint\lb

		\begin{center}
			\begin{statsbox}[width=0.65\linewidth]{Internal Forces}
				\centering
				\input{../../pikz/06ERB/tenscomp5.tex}
			\end{statsbox}
		\end{center}
	}
	 Why do internal forces pull towards each other when the member is in tension? It is because external forces are trying to `stretch' the member and the internal forces are opposing this stretch, maintaining the length of the member.\parm

	 Similarly, when a straight two-force member is in compression, internal forces in the member `push back' against the external compression.\parm

	 Furthermore, at the ends of the two-force members, external and internal forces must be equal and opposite to each other to maintain equilibrium.

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


	\begin{frame}{A Second Look at Strut/Link Connections}

		\def\scale{0.5}
		\begin{textblock*}{1\textwidth}(1.5 cm, 1.5 cm)
					\input{../../pikz/06ERB/strutConnectionB.tex}
		\end{textblock*}

		\begin{textblock*}{0.8\textwidth}(2cm, 7cm)
			\only<1>{
			When strut $AB$ is in {\bfseries tension} (due to forces in $AC$), it `pulls' back against $AC$ to maintain equilibrium.
			}
			\only<2>{
			When strut $AB$ is in {\bfseries compression} (due to forces in $AC$), it `pushes' against $AC$ to maintain equilibrium.
			}
			\uncover<3>{
			Frequently, we don't know in advance whether $AB$ is in tension or in compression. In that case, we draw the force acting on $AC$ in tension (i.e., arrow directed {\bfseries away} from $AC$). If our calculations determine that $R$ is negative, then $AB$ is in compression.
			}
		\end{textblock*}

	\end{frame}

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
	% \begin{textblock*}{1\textwidth}(1cm, 0.25cm)

		\begin{myexam}{}{}
			\def\scale{0.65}
			\centering
			\input{../../pikz/06ERB/06erb05.tex}
			\cmini[0.85]{
				\centering
				Determine the reactions at $D$ and $E$.\parb
				\textcolor{saitMaroon}{Note}: There are two pinned connections, but there is a single link between $C$ and $D$ so $CD$ is a {\bfseries two-force member}, so the direction of the reaction at $D$ is in the direction of $CD$ and has only one unknown - its magnitude.
			}
			
		\end{myexam}
	% \end{textblock*}

\end{frame}

		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}

		\begin{myexer}{}{}
			\def\scale{0.65}
			\centering
			\input{../../pikz/06ERB/06erb07.tex}
			\cmini[0.8]{
				\centering
				Determine the reactions at $A$ and $E$.
			}
			
		\end{myexer}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
	
%
		\begin{myexer}{}{}
			\def\scale{0.65}
			\centering
			\input{../../pikz/06ERB/06erb17.tex}
			\cmini[0.8]{
				\centering
				Determine the reactions at $A$ and $B$.
			}
		
		\end{myexer}
	
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}