\documentclass[10pt,oneside]{article}

\usepackage{amsmath}
\usepackage{bm}
\usepackage{mathpazo}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage[x11names, svgnames]{xcolor} % for \definecolor

\usepackage[letterpaper]{geometry}
\geometry{verbose,tmargin=0.25in,bmargin=0.5in,lmargin=1in,rmargin=1.15in}

\input{../../includes/definedColors.tex}
\input{../../includes/macros.tex}
\input{../../includes/Member.tex}
\input{../../includes/PC.tex}
\input{../../includes/EyeConnection.tex}
\input{../../includes/EyeBolt.tex}

% https://tex.stackexchange.com/questions/731957/how-to-supress-missing-character-there-is-no-u003b-in-font-nullfont
\tracinglostchars=1

\hfuzz=150pt
\setlength{\parindent}{0pt}
\def\scale{1}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% page 1
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{textblock*}{7.25in}(1in, 0.4in)
	\begin{tikzpicture}[line width=0.1mm]
		\draw[color=gray!50, step=0.25in] (0,0) grid +(7.25in,10.25in);
	\end{tikzpicture}
\end{textblock*}


\begin{textblock*}{6.775in}(1in, 0.225in)
  \cbox{
    \centering\huge
    \textbf{Engineering Statics - 02 Force Vectors Handout}
  }
\end{textblock*}

\begin{textblock*}{4in}(1in, 1in)
	\cbox{
		\underline{Example 1} \parm
			      % A displacement is a change in position. It has a magnitude (the distance moved) and a direction, so displacement is a vector quantity.\parb
			      A truck drives due east on a straight road for 40 km, then drives north on a straight road for 30 km before stopping. \parb
			      What is the resultant displacement of the truck?

	}
\end{textblock*}

\begin{textblock*}{4in}(1in, 5in)
	\cbox{
		\underline{Example 2} \parm
		A plane flies NNW (i.e., $22.5\deg$ west of north) with a velocity of $275\text{ km/h}$. There is a wind blowing at $55\text{ km/h}$ from the NW \lb(i.e., $45\deg$ west of north).
			      \parb Determine the resultant velocity of the plane relative to the ground.
			      \parb Determine the wind speed that would cause the plane to fly due north. What is the ground speed in this case?

	}
\end{textblock*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% page 2
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

.\newpage
\begin{textblock*}{7.25in}(1in, 0.4in)
	\begin{tikzpicture}[line width=0.1mm]
		\draw[color=gray!50, step=0.25in] (0,0) grid +(7.25in,10.25in);
	\end{tikzpicture}
\end{textblock*}

\begin{textblock*}{3.5in}(1in, 0.225in)
	\cbox{
		\underline{Example 3} \parm
		Determine the magnitude and the direction (measured clockwise from the the positive $x$-axis) of the resultant of the two forces.

	}
\end{textblock*}
\begin{textblock*}{2.75in}(5.03in, 0.225in)
	\def\scale{0.95}
	\cbox{
		\centering
		
		\input{../../pikz/02ForceVectors/fv21handout.tex}
	}
\end{textblock*}

\begin{textblock*}{3in}(1in, 5in)
	\cbox{
		\underline{Exercise 1} \parm
		The resultant of the forces $F$ and $F_1$ is $3.14$ kN at $37\deg$ clockwise from the
					positive $x$ axis.\parm
					Determine $F$ and $\theta$.

	}
\end{textblock*}
\begin{textblock*}{3.25in}(4.525in, 5in)
	\cbox{
		\centering
		\def\scale{0.8}
		\input{../../pikz/02ForceVectors/fv23handout.tex}
	}
\end{textblock*}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% page 3
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
.\newpage
\begin{textblock*}{7.25in}(1in, 0.4in)
  % \textblockcolor{pink}
	\begin{tikzpicture}[line width=0.1mm]
		\draw[color=gray!50, step=0.25in] (0,0) grid +(7.25in,10.25in);
	\end{tikzpicture}
\end{textblock*}

\begin{textblock*}{4in}(1in, 0in)
	\cbox{
		\underline{Example 4} \parm
		The weight, $W$, of the traffic lights (with mass $105\;\text{kg}$) acts vertically downward.
					\parm
					Find the value of $ W$ and use it to determine the magnitudes of its two components directed along the axes of $AC$ and $BC$.

	}
\end{textblock*}
\begin{textblock*}{2.25in}(5.525in, 0in)
	\cbox{
		\centering
		\scalebox{1.25}{\input{../../pikz/01MathReview/math11handout}}
		
	}
\end{textblock*}

\begin{textblock*}{2.5in}(1in, 5in)
	\cbox{
	\underline{Exercise 2} \parm
		Resolve the $4.20$ kN load suspended from $A$ into components parallel to the truss members $AB$ and $AG$.
		\parm
		Give the magnitude of the components and their direction measured counter-clockwise from the positive $x$ axis.

	}
\end{textblock*}
\begin{textblock*}{3.75in}(4.025in, 5in)
	\cbox{
		\centering
		\scalebox{0.8}{
			\input{../../pikz/02ForceVectors/fv22handout.tex}
		}
	}
\end{textblock*}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% page 4
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
.\newpage
\begin{textblock*}{7.25in}(1in, 0.375in)
	\begin{tikzpicture}[line width=0.1mm]
		\draw[color=gray!50, step=0.25in] (0,0) grid +(7.25in,10.25in);
	\end{tikzpicture}
\end{textblock*}

\begin{textblock*}{3.75in}(1in, 0.235in)
	\cbox{
		\underline{Exercise 3} \parm
		The decoration suspended at $D$ weighs $1120\,\mathsf{N}$.\parm 
				Determine the magnitudes of the two force components of the weight of $D$, in the direction of $AB$ and $BC$.

	}
\end{textblock*}
\begin{textblock*}{2.5in}(5.275in, 0.235in)
	\cbox{
		\centering
		\def\scale{0.8}
		\input{../../pikz/02ForceVectors/fv27handout.tex}
	}
\end{textblock*}

\begin{textblock*}{4.25in}(1in, 5.25in)
	\cbox{
	\underline{Example 5} \parm
	\begin{enumerate}[{a)}]
		\item Determine the resultant $\bm R $ of the two vectors $\bm F$ and $\bm G $.
		\item Determine the $x$-component of $\bm R$ \lb(i.e., the horizontal component).
		% \item Determine the $y$-component of ${\bm{\mathrm{ R }}}$ \lb(i.e., the vertical component).
		\item Determine the $x$-component of $\bm F$.
		\item Determine the $x$-component of $\bm G$.
		\item Add the two previous results.
	\end{enumerate}

	}
\end{textblock*}
\begin{textblock*}{2in}(5.765in, 5.25in)
	\cbox{
		\centering
		\input{../../pikz/02ForceVectors/fv28handout.tex}
	}
\end{textblock*}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% page 5
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
.\newpage
\begin{textblock*}{7.25in}(1in, 0.375in)
	\begin{tikzpicture}[line width=0.1mm]
		\draw[color=gray!50, step=0.25in] (0,0) grid +(7.25in,10.25in);
	\end{tikzpicture}
\end{textblock*}

\begin{textblock*}{4.25in}(1in, 0.235in)
	\cbox{
		\underline{Exercise 4} \parm
		\begin{enumerate}[{a)}]
			\item Determine the magnitude of the component of ${\bm{\mathrm{ R }_{}}}$  along the $y$ axis (i.e., the vertical component).
			\item Determine the magnitude of the component of ${\bm{\mathrm{ F }_{}}}$ along the $y$ axis.
			\item Determine the magnitude of the component of ${\bm{\mathrm{ G }_{}}}$ along the $y$ axis.
			\item Add the two previous results.
		\end{enumerate}

	}
\end{textblock*}
\begin{textblock*}{2in}(5.765in, 0.235in)
	\cbox{
		\centering
		\input{../../pikz/02ForceVectors/fv28handout.tex}
	}
\end{textblock*}

\begin{textblock*}{3in}(1in, 6.25in)
	\cbox{
	\underline{Example 9} \parm
		Determine the resultant (magnitude and direction counterclockwise from the positive $x$ axis) of the three forces $F_1,\;F_2$ and $F_3$ acting at a single point.

	}
\end{textblock*}
\begin{textblock*}{3.25in}(4.525in, 6.25in)
	\cbox{
	\def\scale{0.8}
	\centering
	\input{../../pikz/02ForceVectors/fv24handout}
	}
\end{textblock*}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% page 6
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
.\newpage
\begin{textblock*}{7.25in}(1in, 0.375in)
	\begin{tikzpicture}[line width=0.1mm]
		\draw[color=gray!50, step=0.25in] (0,0) grid +(7.25in,10.25in);
	\end{tikzpicture}
\end{textblock*}

\begin{textblock*}{3.5in}(1in, 0.235in)
	\cbox{
		\underline{Example 10} \parm
		The resultant of the forces $F,\;F_1$ and $F_2$ acting upon the eye-bolt is $3.07$ kN at $197\deg$ measured counter-clockwise from the positive $x$ axis. Determine $F$ and $\theta$.

	}
\end{textblock*}
\begin{textblock*}{2.75in}(5.025in, 0.235in)
	\cbox{
	\def\scale{0.8}
	\centering
	\input{../../pikz/02ForceVectors/fv25handout}
	}
\end{textblock*}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% page 7
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% .\newpage
% \begin{textblock*}{7.25in}(1in, 0.375in)
% 	\begin{tikzpicture}[line width=0.1mm]
% 		\draw[color=gray!50, step=0.25in] (0,0) grid +(7.25in,10.25in);
% 	\end{tikzpicture}
% \end{textblock*}



\end{document}