
%!TEX option = --shell-escape

\documentclass[9pt, xcolor={svgnames, x11names},professionalfonts]{beamer}


\input{../../includes/macros}
\input{../../includes/definedColors}
\input{../../includes/Channel.tex}
\input{../../includes/Couple.tex}
\input{../../includes/DL.tex}
\input{../../includes/EyeBolt.tex}
\input{../../includes/EyeConnection.tex}
\input{../../includes/Member}
\input{../../includes/Mem}
\input{../../includes/Meme}
\input{../../includes/PC}
\input{../../includes/Ring}
\input{../../includes/Rocker}
\input{../../includes/Roller}
\input{../../includes/Pulley}
\input{../../includes/PulleyB}
\input{../../includes/PulleyC}
\input{../../includes/Luke.tex}
\input{../../includes/Skywalker.tex}
\input{../../includes/WBeam.tex}
% \input{../../includes/includesExisting/tikzObjects.tex}

\setlength{\parindent}{0pt}
\setlength{\parskip}{\medskipamount}


\tcbset{fonttitle=\itshape\rmfamily}
\usepackage{mathpazo}
 
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usefonttheme[onlymath]{serif} % this needs to be before structureitalicserif?
\usefonttheme{structureitalicserif} %make titles fancy ;-)


\usecolortheme[named=statsMaroon]{structure}
\setbeamertemplate{navigation symbols}{} % remove navigation symbols
\setbeamertemplate{headline}{\vspace{0.125cm}}
\setbeamertemplate{footline}{ \hfill \insertshorttitle\qquad \insertsection \qquad \insertframenumber/\inserttotalframenumber\quad{ }\vspace{0.125cm}}
\setbeamertemplate{items}[default]
\setbeamertemplate{blocks}[shadow=true]

\setbeamercolor{title}{bg=statsMaroon, fg=Azure}
\setbeamercolor{frametitle}{fg=white, bg=statsMaroon}
\setbeamercolor{background canvas}{bg=Gainsboro!50}
\setbeamercolor{block title}{bg=statsMaroon, fg=white}
\setbeamercolor{block body}{bg=white, fg=black}

\setlength{\parskip}{\medskipamount}
\setlength{\parindent}{0pt}

% https://tex.stackexchange.com/questions/731957/how-to-supress-missing-character-there-is-no-u003b-in-font-nullfont
\tracinglostchars=1
\hfuzz 120pt

\def\scale{1}
\newcounter{examnumber}
\newcounter{exernumber}
%test
\resetcounteronoverlays{tcb@cnt@myexam}
\resetcounteronoverlays{tcb@cnt@myexer}
% \newcounter{myexercisecounter}

% Title page details: 
\title[Moments \& Couples]{\Huge 05 Moments and Couples}
\subtitle[Engineering Statics]{\Large\textcolor{white}{Engineering Statics}}
\author{}
\date{\small Updated on: \today}

% \raggedright

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[plain]    %don't need footer on titlepage
	\titlepage
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Bodies}

	\begin{textblock*}{9cm}(2cm,1.25cm)
		\begin{itemize}
			\only<1>{
				\item So far, we have concerned ourselves with forces acting at a single point (or particle)\parm			
				\item We now start to look at non-concurrent forces, where several forces act upon a body but at different locations.
			}
			\only<2>{
				\item Consider the forces acting on the beam:
				\item How can the teeter-totter balance when the force due to Wendy's weight is more than twice that of her younger brother?
				\item As children, we all figured out that the solution involved the heavier person sitting closer to the fulcrum (the balance point); this was one of our first introdutions to {\bf moments}.
			}
			\only<3>{
				\item A moment is a measure of a tendency to rotate. (It is the same as torque.)
				\item The teeter-totter  will balance (that is, it is equilibrium) when counterclockwise moment due to Wendy equals the clockwise moment due to her little brother.
				\item That is, when the tendency to rotate in the counter-clockwise direction is equal to the tendency to rotate in the clockwise direction.
			}
			\only<4-5>{
				\item Moments, then, are related to force and to distance!
				\item In general, when a force is applied to a structural body, there is a tendency for that body to rotate.
			}
			\only<5>{
				\item {\bfseries Important}: We assume structural bodies are rigid -- they do not deform under load. Also, unless otherwise stated, structural bodies are assumed to have negligible weight compared to the forces applied to them.
			}
			
		\end{itemize}
	\end{textblock*}
	\begin{textblock*}{8cm}(3cm, 5cm)	
		
		\begin{statsbox}{}		
			\centering
			\vspace{-0.25cm}
			\input{../../pikz/05Moments/05Moments01.tex}		
		\end{statsbox}
		
	\end{textblock*}
\end{frame}

\begin{frame}{Why Two Equations Are Not Enough...}
	\begin{itemize}
		\item Consider a simple body, subject to two forces, equal in magnitude and opposite in direction:
	\end{itemize}

	\def\scale{0.65}
	\begin{center}
		\tcbox[colback=white,boxsep=0pt,top=15pt,bottom=15pt,left=5pt,right=5pt, enhanced, drop fuzzy shadow,colframe=structure]{
			\input{../../pikz/05Moments/05Moments02.tex}
		}
	\end{center}

	\begin{itemize}
		\item<2-> $\Sigma F_x=0$ and $\Sigma F_y=0$, but, clearly, this body is not in equilibrium; it will rotate in a counter-clockwise direction.
		\item<3-> To consider equilibrium for non-concurrent forces, {\bfseries moments} must be taken in to account.
	\end{itemize}
\end{frame}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Moments}
	\def\scale{0.75}
	\begin{center}
		\tcb[left=5mm, right=5mm]{
			\centering
			\input{../../pikz/05Moments/05Moments03.tex}
		}

	\end{center}
	\cmini[0.9]{
		\small
		Another lesson we learned as we were growing up was that is was easier to open a door by pushing or pulling on the handle that was further from the door hinges than it was to push close to the hinges.
	}

\end{frame}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Moments}

	\cmini[0.8]{
		\begin{statsbox}[title=Definition of a Moment]{}{%
				The {\bfseries moment} $M_O$ of a force $F$ about a point $O$ is given by:
				$$\bm{ M=Fd} $$
				where $d$ is the {\bfseries perpendicular} distance from $O$ to the line of action of the force $F$. ($d$ is known as the {\bf moment-arm}.)}
		\end{statsbox}
		\parb
		\mini[0.45]{
			\tcbox[colback=white,boxsep=0pt,top=15pt,bottom=15pt,left=5pt,right=5pt, enhanced, drop fuzzy shadow,colframe=structure]{
				\def\scale{0.3}
				\centering
				\input{../../pikz/05Moments/05Moments04.tex}
			}
		}
		\hfill
		\mini[0.5]{
			Moments are a product of force and distance so units are $\mathsf{N\cdot mm}$, $\mathsf{N\cdot m}$, $\mathsf{kN\cdot m , \, ft\cdot lb,\, in\cdot lb, \ldots} $
			\parb
			{\bfseries Sign Convention}:\lb
			If the tendency to rotate about $O$ is counter-clockwise, the moment is {\bfseries positive}. \par If clockwise, the moment is {\bfseries negative}.
		}
	}
\end{frame}


\begin{frame}

	\begin{myexam}{}{}
		\mini[0.45]{
			\centering
			\def\scale{0.6}
			\input{../../pikz/05Moments/05Moments08.tex}
		}
		\hfill
		\mini[0.5]{
			Determine the moment, $M_A$, of the $3.5$ kN force applied at $B$, about the point $A$.			
		}
	\end{myexam}
\end{frame}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}

	\begin{myexam}{}{}
		\mini[0.5]{
			\def\scale{0.65}
			\parb
			\input{../../pikz/05Moments/05Moments09.tex}
		}
		\hfill
		\mini[0.4325]{
			Determine the sum of the moments of the forces, acting at $B$ and $C$, about the point $A$. \parm  Also, sum the moments of the forces about the point $B$.

		}
	\end{myexam}
\end{frame}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{}

	\begin{myexer}{}{}
		\def\scale{0.65}
		\input{../../pikz/05Moments/05Moments11.tex}
		\cmini[0.9]{
			Rigid beam $ABCD$ is supported at $A$ and at $D$, and is subjected to the two forces shown at $B$ and $C$.\parm
			Determine the value of the reaction at $D$, $R_D$, if the sum of the moments about $A$, $\Sigma M_A$, is zero and the reaction at $D$ is vertically upwards.
		}
	\end{myexer}
\end{frame}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{The Principle of Moments}
	The Principle of Moments,  often referred to as Varignon's Theorem, is stated~below:\parm
	\begin{statsbox}[title=Varignon's Theorem, left=5mm, right=5mm]
		\centering
		The moment of a force about a point  is equal to the sum of the moments of the components of the force about the same point.
	\end{statsbox}
	\parb
	In many cases, it is more convenient to sum the moments of a forces components than it is to use the formula directly.

	There are two primary ways we use this result:
	\begin{itemize}
		\item Resolve the force into horizontal and vertical components
		\item Resolve the force into orthogonal (perpendicular to each other) components, with the line of action of one component passing through the point about which we are taking moments -- so that its moment is zero ($d=0$).
	\end{itemize}

	% \cmini[0.8]{
	% 	\footnotesize
	% 	\textcolor{saitMaroon}{(Another Varignon's Theorem, attributed to the same French mathematician, is a delightful result for those interested in geometry: the midpoints of the sides of any quadrilateral (four-sided polygon) form the vertices of a parallelogram. Furthermore, the area of the parallelogram is half that of the quadrilateral! :)}
	% }
\end{frame}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \begin{frame}{}
% 	\begin{myexam}{}{}
% 		\def\scale{0.75}
% 		\input{../../pikz/05Moments/05Moments13.tex}
% 		\cmini[0.9]{
% 			The truss shown is supported by a pinned connection at $A$ and a roller (on a plane inclined at $25^\circ$ to the horizontal) at $D$. Determine the magnitude and direction of $R_D$, the reaction at $D$, if the sum of the moments about $A$ is zero.
% 		}
% 		% \begin{center}
% 		% 	\footnotesize
% 		% 	\rotatebox[origin=c]{180}{
% 		% 		\textcolor{gray}{
% 		% 			($R_D=1.98\,\mathsf{kN}$)
% 		% 		}
% 		% 	}
% 		% \end{center}

% 	\end{myexam}
% \end{frame}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
	\cmini{
		\begin{myexam}{}{}
			\centering\parb
			\input{../../pikz/05Moments/05Moments05.tex}
			\parb
			Determine the moment about $A$ of the force applied to $B$ by resolving the force at $B$ into horizontal and vertical components.
		\end{myexam}
	}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
	\cmini[1]{
		\begin{myexam}{}{}
			\def\scale{0.6}
			\centering
			\input{../../pikz/05Moments/05Moments08.tex}
			\parm
			\raggedright
			
			\ccbox[0.8]{Cornsilk3}{Cornsilk3}{\small (Revisiting {\itshape\rmfamily Example 1}.) Notice that we cannot calculate the moment about $A$ of the force acting on $B$ using horizontal and vertical components because, without the angle at which $AB$ is inclined, we cannot determine the moment arm, $d$, for either the horizontal or the vertical component.} 
			\parm\centering
			Determine the moment about $A$ of the force at $B$ by resolving the force into components parallel to and perpendicular to $AB$.
		\end{myexam}
	}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
	\cmini[1]{
		\begin{myexer}{}{}
			\def\scale{0.8}
			\centering\parb
			\input{../../pikz/05Moments/05Moments06.tex}
			\parm	
			Determine the moment about $A$ of the force acting at $C$. \lb Then determine the moment about $B$ for the same force.
		\end{myexer}
	}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
	\cmini[1]{
		\begin{myexer}{}{}
			\def\scale{0.8}
			\centering
			\input{../../pikz/05Moments/05Moments07.tex}
			\parm	
			\cmini[0.7]{
				\centering
				Determine the sum of the moments about $A$, about $C$ and about $F$, of the forces shown.
			}
			
		\end{myexer}
	}
\end{frame}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Moments of Force Couples}
	\cmini[0.9]{
		\begin{itemize}
			\item  In the previous exercise, we found that the moments were the same about any of the points used.
			\item 	Also, the forces are different: there is an equal and opposite pair with magnitude $1690\,$N and an equal and opposite pair with magnitude $1020\,$N.
			\item Such pairs of forces, with parallel lines of action, equal magnitude and opposite sense are called force {\bfseries couples}.
			\item The resultant force of a couple is zero: $\Sigma F_x=0$ and $\Sigma F_y=0$.
			\item The {\bfseries moment of a couple}, irrespective of any point, has magnitude
			      \cmini[0.6]{
			      	\begin{statsbox}{A Couple Defined:}
			      		$$ M=F\cd d $$
			      		\centering
								\cmini{
									\centering
									where $d$ is the distance between the two lines of action.
								}
			      		
			      	\end{statsbox}
			      }
			\item Clockwise couples are considered negative, counter-clockwise couples are considered positive.
		\end{itemize}
	}
\end{frame}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
		\begin{myexam}{}{}
			\centering
			\def\scale{0.8}
			\parb
			\input{../../pikz/05Moments/05Moments07.tex}
			\parm
			Determine $\Sigma M$, the sum of the moments, of the couples shown.
		\end{myexam}
\end{frame}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}

	\begin{myexam}{}{}
		\def\scale{0.5}
		\begin{center}
			\input{../../pikz/05Moments/05Moments14.tex}
		\end{center}
		\cmini[0.7]{
			\parb
			Considering beam $AB$:
			\begin{enumerate}
				\item Determine the magnitude of $R_D$ if $\Sigma M_A=0$.
				\item Determine the magnitude of $R_{Ay}$ if $\Sigma F_y=0$.
				\item Determine the magnitude of $R_{Ax}$ if $\Sigma F_x=0$.
			\end{enumerate}
			
		}
	\end{myexam}
\end{frame}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}

	\begin{myexer}{}{}
		\def\scale{0.5}
		\begin{center}
			\input{../../pikz/05Moments/05Moments15.tex}
		\end{center}
		\cmini[0.8]{
			\parb
			$ABCD$ has a negative couple applied at $B$ and is supported by a cable at $D$. 
			\begin{enumerate}
				\item Determine the magnitude of $T$ if $\Sigma M_A=0$.
				\item Determine the reaction at $A$ if $\Sigma F_x = \Sigma F_y =0$.				
			\end{enumerate}
			
		}
	\end{myexer}
\end{frame}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{frame}{Distributed Loads}

	\begin{textblock*}{1\textwidth}(1cm, 1.25cm)
		\begin{tcolorbox}[colback=white,colframe=structure,top=0pt, bottom=5pt, enhanced, drop fuzzy shadow]
			\input{../../pikz/05Moments/05dl01.tex}
		\end{tcolorbox}

		\begin{itemize}
			\only<1>{
				\item Consider a rigid beam $ABC$ with individual loads concentrated at separate locations. We have found the moments of forces like these.
			}
			\only<2>{
				\item Suppose, instead, that three W150 X 13 beams are placed on $ABC$.
				\item If all the beams are rigid (as we assume in statics), then the weight of the load is distributed uniformly to $ABC$ along the length of the three W150~X~13 beams
				\item This kind of load is known as a {\bf uniformly distributed load} (UDL).
				}\only<3-4>{
				\item Now, assume the three beams are each $4.00\thinspace\text{m}$  in length. \lb
				The total mass, $m$, and weight, $W$, of the three beams is given by:
				\begin{align*}
					m & = 3\;@\;4.00\text{ m} \times 13\thinspace\text{kg} = 156\thinspace\text{kg}   \\
					W & = 156\thinspace\text{kg} \times 9.81\mathsf{\thinspace m/s^2} = 1530\text{ N}
				\end{align*}
				
				}\only<4>{
					\item This force is spread out uniformly over $4.00\thinspace\text{m}$ so the distributed load is $382.50\text{ N/m}$.
					\item Note that distributed loads have units force/length: {\bfseries N/m}, {\bfseries lb/ft}.
			}
			\only<5>
			{
				\item Uniformly distributed loads are drawn as shown.
			}
			\only<6>{
				\item Distributed loads need not be uniform. They can be {\bfseries uniformly varying loads} (UVL).
				\item Note that uniformly varying loads vary at a constant rate so they have a triangular shape, with a constant slope.\parm\small
				(Distributed loads may also defined as $f(x)$, a function of $x$ where $x$ is the distance along the load, and may follow fairly complex curves that require integration to solve: we shall not cover these in this course.)
			}
		\end{itemize}
	\end{textblock*}

\end{frame}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Magnitude and Resultant of Distributed Loads}
	In both cases, the magnitude of the resultant force is given by the area of the rectangle or triangle, and the resultant acts through the centroid of the area.\parb
	\mini[0.47]{
		\begin{statsbox}{Uniformly Distributed Load}
			\begin{center}
				\input{../../pikz/05Moments/05dl02.tex}
			\end{center}
		\end{statsbox}
	}
	\hfill
	\mini[0.48]{
		\begin{statsbox}{Uniformly Varying Load}
			\begin{center}
				\input{../../pikz/05Moments/05dl03.tex}
			\end{center}
		\end{statsbox}
	}

\end{frame}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Distributed Loads}
	\begin{myexam}{}{}
		\centering
		\input{../../pikz/05Moments/05dl04.tex}
		\parm
		Determine the moment of the distributed load about  $O$.
		\parm
		% answers, gray, centered, upside down
		% \begin{center}
		% 	\footnotesize
		% 	\textcolor{gray}{
		% 		\rotatebox[origin=c]{180}{
		% 			($-50.0\,\mathsf{kN\!\cdot\! m}$)
		% 		}
		% 	}
		% \end{center}
	\end{myexam}
	\centering
	% For a more dynamic, conceptual view of these types of loadings, look \href{http://eduk8r.org/jsSims/statics/loads/index.html}{here}.

\end{frame}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Distributed Loads}

	\begin{myexer}{}{}
		\centering\def\scale{1.25}
		\input{../../pikz/05Moments/05Moments16.tex}
		\parm
		Determine the moment of the distributed load about  $(0,0)$.
		\parm
		% answers, gray, centered, upside down
		% \begin{center}
		% 	\footnotesize
		% 	\textcolor{gray}{
		% 		\rotatebox[origin=c]{180}{
		% 			( $13.9\,\mathsf{kN\!\cdot\!m}$ )
		% 		}
		% 	}
		% \end{center}
	\end{myexer}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}